\begin{thebibliography}{20}

\bibitem{mengoni}
  D. Mengoni et al.,
  \emph{Digital pulse-shape analysis with a TRACE early silicon prototype}, Nucl. Instrum. Meth. A764 (2014), 241-246.

\bibitem{galileo}
  D. Testov, J.J. Valiente-Dobón, D. Mengoni, F. Recchia, A. Goasduff, A. Boso, S. Lenzi, G. de Angelis, S. Lenzi et al.
  \emph{High resolution $\gamma$-ray spectroscopy using GALILEO array}, arXiv:1903.01296.
  
\bibitem{oko:cluster}
  J. Okolowicz, M. Ploszajczak and W. Nazarewicz,
  \emph{On the origin of nuclear clustering}, Prog. Theor. Phys. Supplement 196 (2012) 230.

\bibitem{oko:origin}
  J. Okolowicz, M. Ploszajczak and W. Nazarewicz,
  \emph{Toward understanding the microscopic origin of nuclear clustering}, Fortschr. Phys. 61, 66 (2013).

\bibitem{strano}
  E. Strano et al., Nucl. Instrum. Methods, B317 (2013) 657.
  

\bibitem{salathe}
Salathe, Marco, and Thomas Kihm. 
\emph{Optimized Digital Filtering Techniques for Radiation Detection with HPGe Detectors}, Nucl. Instrum. Meth. A808 (2016): 150–155.

\bibitem{tensorflow}
Martín Abadi, Ashish Agarwal, et al.
\emph{TensorFlow: Large-scale machine learning on heterogeneous systems},
2015. Software available from tensorflow.org.

\bibitem{pytorch}
Adam Paszke, Sam Gross et al.
\emph{Automatic differentiation in PyTorch},
2017

\bibitem{ml4phys}
Mehta, Pankaj et al. 
\emph{A High-Bias, Low-Variance Introduction to Machine Learning for Physicists.}, Physics Reports 810 (2019): 1–124. Crossref. Web.

\bibitem{baldi}
Baldi, Pierre, Peter Sadowski, and Daniel Whiteson, \emph{Searching for exotic particles in high-energy physics with deep learning}, Nature communications 5 (2014), 4308.

\bibitem{williams}
Williams, J. Michael. \emph{Machine Learning in HEP}, No. LHCb-TALK-2015-338. 2015.

\end{thebibliography}
